---
title: "week_02_day3_sql_lab_homework"
output: html_notebook
---


```{r}
library(RPostgreSQL)
```
# Setup a connection from R to your local omni_employees database, then write a single query to solve each of the following problems:
```{r}

home_location <- Sys.getenv("HOME")
credentials_location <- paste0(home_location,"/credentials.R")
source(credentials_location)

```



```{r}
db_connect <- dbConnect(drv = PostgreSQL(), user = postgresql_username, password = postgresql_password, dbname = "omni_employees", host = "localhost")
rm(postgresql_username, postgresql_password)
```


2.1 Find all the employees who work in the ‘Human Resources’ department.







# first find out what data contains, so I will use the DISTINCT function

```{sql connection=db_connect}
SELECT 
DISTINCT(department)
FROM employees 
```

```{sql connection=db_connect}
SELECT *
FROM employees
WHERE department = 'Human Resources'
```



2.2 Get the first name, last name, and country of the employees who work in the ‘Legal’ department


# selecting first_name,last_name and country, from employees and then specifying what area.  
```{sql connection=db_connect}
SELECT 
  first_name,
  last_name,
  country
  FROM employees
  WHERE department = 'Legal'
  
```
Q3. Count the number of employees based in Portugal.

# using the count function
```{sql connection=db_connect}
SELECT 
  COUNT(id) AS employees_from_portugal
  FROM employees 
  WHERE country = 'Portugal'

```
Q4 Count the number of employees based in either Portugal or Spain.

```{sql connection=db_connect}
SELECT 
  COUNT(id) AS employees_from_portugal_or_spain
  FROM employees 
  WHERE country IN ('Portugal','Spain')
```

Q5 Count the number of pay_details records lacking a local_account_no

#look at the data using distinct 

```{sql connection=db_connect}
SELECT 
DISTINCT(pay_detail_id)
FROM employees

```

```{sql connection=db_connect}
SELECT 
  COUNT(id) AS missing_account_number
  FROM pay_details
  WHERE local_account_no IS NULL
```
Q6 Are there any pay_details record lacking both a local_account_no and iban number?


```{sql connection=db_connect}
SELECT 
  COUNT(id) AS missing account_no
  FROM employees
  WHERE local_account_no IS NOT TRUE
  

```


Q7 Get a list of employees first names and last names ordered alphabetically by their last name (put any nulls last).



```{sql connection=db_connect}
SELECT
  first_name,
  last_name,
  country
  FROM employees
  ORDER by last_name
  
```


8. Get a list of employees first names, last names and countries, ordered alphabetically first by their country and second by their last name (put any nulls last).


```{sql connection=db_connect}
SELECT
  first_name,
  last_name,
  country
  FROM employees
  ORDER by country,last_name
```

Q9 Find the top ten highest paid employees in the corporation.




```{sql connection=db_connect}
SELECT *

FROM employees
WHERE salary IS NOT NULL
ORDER BY salary DESC
LIMIT 10
```

Q11 Find the first name, last name and salary of the lowest paid of the employees in Hungary

```{sql connection=db_connect}
SELECT 
  first_name,
  last_name,
  salary, 
  country
FROM employees
WHERE country = 'Hungary'
ORDER by salary ASC

```

Q11 . How many employees have a first name beginning with ‘F’?

```{sql connection=db_connect}
SELECT *
FROM employees
WHERE first_name LIKE 'F%'
```
Q12 Find all the details of any employees with a ‘yahoo’ e-mail address?

```{sql connection=db_connect}
SELECT *
FROM employees
WHERE email LIKE '%yahoo%'
```

Q13 Count the number of pension enrolled employees not based in either France or Germany.


```{sql connection=db_connect}
SELECT 
 count(id) AS employees_with_pension_rm_france_germany
 FROM employees
WHERE pension_enrol = TRUE AND country IN ('France', 'Germany')




```



Q14 Breakdown the numbers of employees enrolled, not enrolled and whose enrollment status is unknown in the corporation pension scheme.



```{sql connection=db_connect}
SELECT
DISTINCT(pension_enrol)
FROM employees

```


```{sql connection=db_connect}
SELECT 
  pension_enrol,
  COUNT(id) AS number_of_employees
  FROM employees
WHERE pension_enrol IN ('TRUE', 'FALSE') OR pension_enrol IS NULL
GROUP BY pension_enrol
```



15. What is the maximum salary among employees in the Engineering department who work 1.0 full-time equivalent hours?

```{sql connection=db_connect}
SELECT
DISTINCT(department)
FROM employees
```


# selecting the columns I would like displayed or think is releventto be displayed and running the WHERE condition to specify department abd fte_hours. 
#ordering by salary in descending order and limiting the rows to 10


```{sql connection=db_connect}
SELECT 
  id,
  first_name,
  last_name,
  fte_hours, 
  salary,
  department
FROM employees
WHERE department = 'Engineering' AND fte_hours = ('1.0')
ORDER by salary DESC
LIMIT 10
```

Q16. Obtain a count by department of the employees who started work with the corporation in 2003.


group by deparmtent 
```{sql connection=db_connect}
SELECT 
  department,
COUNT(id) AS number_of_employees_starting_in_2003
FROM employees
WHERE start_date BETWEEN '2003-01-01' AND '2003-12-31'
GROUP BY department 
ORDER BY number_of_employees_starting_in_2003 DESC
```


```{r}
dbDisconnect(db_connect)
```



