---
title: "R Notebook"
output: html_notebook
---

Question 1.

Create a vector called stock_prices with the following data points: 23, 27, 23, 21, 34, 24, 25, 30, 37, 30.

```{r}
stock_prices <- c(23,27,23,21,34,24,25,30,37,30)
stock_prices
```


Create a vector called day_of_week, which repeats Monday to Friday twice. i.e. ‘Monday’, ‘Tuesday’, ‘Wednesday’, ‘Thursday’, ‘Friday’, ‘Monday’, ‘Tuesday’, ‘Wednesday’, ‘Thursday’, ‘Friday’.

day_of_week <- rep("Monday","Tuesday","Wednesday","Thursday","Friday", each=2)
```{r}
day_of_week <- c("Monday","Tuesday","Wednesday","Thursday","Friday")
day_of_week
```
```{r}
day_of_week_pepper <- rep(day_of_week, times=2)
day_of_week_pepper

```


Question 2.

Create a vector called day_of_week_factor, which has the same data as day_of_week, but is of factor type.

```{r}
day_of_week_factor <- as.factor(c("Monday","Tuesday","Wednesday","Thursday","Friday","Monday","Tuesday","Wednesday","Thursday","Friday"))

day_of_week_factor
```


Create a vector called named_stock_prices, which contains the stock prices, named by days of the week.

```{r}
named_stock_prices <- data.frame(day_of_week_factor,stock_prices)
named_stock_prices
```




Question 3.

Make a data frame called stock_data containing the stock price and day of the week information, and View() the result.


```{r}
named_stock_prices
```




Question 4.

Make a list called stock_list with named elements as follows: the vector of stock_prices, the vector day_of_week, and the data frame you made in question 3. Choose sensible names for the list elements.

```{r}
stock_list <- list(stock_prices = stock_prices,day_of_week = day_of_week,named_stock_prices = named_stock_prices)
stock_list
```
 Part 2
In this part, you will practice selecting elements from vectors, data frames, matrices and lists.

For Part 2, you need the code you’ve written for Part 1. If you’ve really struggled with this and can’t do it, then the code for Part 1 is listed underneath the hidden button below. Do try your hardest first though before using the code below!




Question 1.

Select the 4th, 5th and 6th stock prices from stock_prices.

```{r}

stock_prices[4:6]
```


Select the stock prices greater than 30 from stock_prices.

```{r}
subset(stock_prices,stock_prices > 30)
```


Question 2.

Select the day_of_week column from the stock_data data frame.


```{r}
stock_data <- data.frame(stock_prices = stock_prices, day_of_week = day_of_week)
```


```{r}
stock_data$day_of_week
```


Select the rows of the stock_data data frame where the stock_prices are less than 25.

Select the 1st column of stock_data.

```{r}
stock_data[ ,1]
```


Select the 3rd row of stock_data.

```{r}
stock_data[3, ]
```


Select the 3rd element in the 1st column of stock_data.

```{r}
stock_data[3,1]
```




Question 4.

Select the data frame from within the list of stocks.
```{r}
list(stock_list$named_stock_prices)
```

