---
title: "R Notebook"
output: html_notebook
---

```{r}
home_location <- Sys.getenv("HOME")
credentials_location <- paste0(home_location,"/credentials.R")
source(credentials_location)
```



```{r}
library(RPostgreSQL)

```

# connecting the local postgresSQL 



```{r}

my_db_connection_mvhbdgdk <- dbConnect(drv = PostgreSQL(max.con = 2), user = wrestling_postgresql_username_local, password = wrestling_postgresql_password_local, dbname = 'mvhbdgdk', host = 'manny.db.elephantsql.com')


```



# return all the wrestlers, 
Using the R connection you just created, write and execute a SQL query to return all the wrestlers in the wrestlers table.

Explore the columns stored in the table. State which data type you think each column stores



```{r}
  dbListFields(conn = my_db_connection_mvhbdgdk, name = "wrestlers")
```
```{r}
wrestler_data <- dbGetQuery(conn = my_db_connection_mvhbdgdk, statement = "SELECT * FROM wrestlers")
wrestler_data
```



# Explore the columns stored in the table. State which data type you think each column stores.

I would predict the data to be 

ID
born = VARCHAR
name = VARCHAR
gender = VARCHAR
win percentage - REAL
total matches - INT


dbDisconnect(conn = my_db_connection)
```{r}
dbDisconnect(conn = my_db_connection_mvhbdgdk)
```

# creating a  REMOTE post gresSQL connection

#run before anything and check that library is loaded.


```{r}
home_location <- Sys.getenv("HOME")
credentials_location <- paste0(home_location,"/credentials.R")
source(credentials_location)
```




```{r}
my_db_connection_mvhbdgdk_remote <- dbConnect(drv = PostgreSQL(max.con = 2), user = wrestling_postgresql_username_remote, password = wrestling_postgresql_password_remote, dbname = 'mvhbdgdk', host = 'manny.db.elephantsql.com')

```


#list all the wrestlers of remote 


```{r}
dbListTables(conn = my_db_connection_mvhbdgdk_remote)

```
#list all the wrestlers of remote 


using the "SELECT * FROM wrestlers", this is down in uppercase. 
```{r}
wrestler_data_remote1 <- dbGetQuery(conn = my_db_connection_mvhbdgdk_remote, statement = "SELECT * FROM wrestlers")

wrestler_data_remote1


```



```{r}
dbListFields(conn = my_db_connection_mvhbdgdk_remote, name = "wrestlers")
```



# disconnect 
```{r}
dbDisconnect(conn = my_db_connection)
```

