---
title: "week 1 day 3 homework"
output: html_notebook
---

```{r}
install.packages('devtools')
devtools::install_github('codeclan/CodeClanData')
library(CodeClanData)
```

```{r}
library(CodeClanData)

```

#viewing the data set and selecting beer part of it.


```{r}
CodeClanData::beer
```




#making beer_percent vector from code clan data set, subsetting using square brackets and selecting 3rd column [, 3]
```{r}

beer_percent <- CodeClanData::beer[ ,3]
beer_calories <- CodeClanData::beer[ ,4]
beer_carbohydrates <- CodeClanData::beer[ ,5]
```





```{r}
beer_percent
beer_calories 
beer_carbohydrates
```
#calculating sum of beer_percent,omitting missing values with na.rm

```{r}
sum(beer_percent, na.rm = FALSE)
```


```{r}
average_percent <- mean(beer_percent)
average_calories <- mean(beer_calories)
average_carbohydrates <- mean(beer_carbohydrates)
```


# convert beer calories to numeric? currently character


```{r}
beer_calories <- as.numeric(beer_calories)
```

#find min and max beer percentage and the range 


```{r}
min_beer_percent <- min(beer_percent)
max_beer_percent <- max(beer_percent)

range_beer_percent <- range(beer_percent)
```

```{r}
min_beer_percent
max_beer_percent

```

#splititng into high, medium and low beer percentage


```{r}
high_percent <- subset(beer_percent, beer_percent >= 4)
medium_percent <- subset(beer_percent, beer_percent >= 4)
low_percent <-subset(beer_percent, beer_percent < 4)
```

```{r}
high_percent
medium_percent
low_percent
```



#plot alcohal percentage and calories

```{r}
plot(beer_calories,alcohal_percentage)
```



#temperature data

```{r}
temp_data <- CodeClanData::temp
temp_data
```


```{r}
january_average <- CodeClanData::temp[ ,1]

```



# mean of each month temperature utilising the colMeans function

```{r}
colMeans(temp_data, na.rm = FALSE,dims = 1 )
```

# trying to plot temperature over the year, however unable to get axis labelled. 


```{r}
 plot(colMeans(temp_data))
main = "Average Temperature Over the Year"
xlab = "time in year"
ylab = "mean temperature"
  
```


