---
title: "week_02_day1_homework"
output: html_notebook
---



```{r}
library(readxl)
library(readr)
library(jsonlite)



```

# read in data

1. Read in the state_income_data.csv file using the appropriate function


```{r}
read_csv("Data/state_income_data.csv")
```



2.How do you specify your own column names when using read_csv()?


```{r}
read_csv("data/state_income_data.csv", col_names =  c("State", "2002", "2003", "2004",   "2005",   "2006", "2007", "2008", "2009", "2010", "2011",  "2012", "2013", "2014", "2015"),skip = 1)
```

3. Read in the cars.csv file and use the col_types() function to ensure you load in:


# Alternatively, you can use a compact string representation where each character represents one column: c = character, i = integer, n = number, d = double, l = logical, f = factor, D = date, T = date time, t = time, ? = guess, or _/- to skip the column.

```{r}


cars <- read_csv("data/cars.csv", col_types = c("ccdddl"))
                

```
```{r}

cars
```





4. Read in the scotland.txt file using the appropriate function.


```{r}
read_file("data/scotland.txt")

class("data/scotland.txt")
```

# better way of doing it is this . 


```{r}
read_lines("data/scotland.txt")
```


5. How do you read text into a one element character vector?

read_lines function
```{r}
read_lines("data/scotland.txt")
```

read_lines("data/scotland.txt")



6. Read in the steam-200k-sample.csv file. Fix any problems you may encounter.



```{r}
read_csv("data/steam-200k-sample.csv",skip = 4)
```


7. Read in the historic_eu_payments.tsv file.


```{r}
eu_payments <- read_tsv("data/historic_eu_payments.tsv")
View(eu_payments)
```


8. How do you read lines of text into a multi-element text vector?


```{r}
read_file()
```


Read in the JSON file from the following url: http://makemeanalyst.com/wp-content/uploads/2017/06/sample_json.txt



```{r}
sample_json <- read_file("http://makemeanalyst.com/wp-content/uploads/2017/06/sample_json.txt")
```

```{r}
sample_json
```


£fromJSON function to read certain functions. 
```{r}
sample_json2<-fromJSON("http://makemeanalyst.com/wp-content/uploads/2017/06/sample_json.txt")


sample_json2
```

