---
title: "Tidyverse consolidation homwork"
output: html_notebook
---




```{r}
library(tidyverse)
library(readr)
library(readxl)
```
1. Load the code_clan_tweets.csv data 
# use the read_csv files to load into data
Find the number of rows, columns, and list all the variable names.clan_tweets
#dimensions and #names function

```{r}
twitter_data <- read_csv("data/code_clan_tweets.csv")
dim(twitter_data)
names(twitter_data)


```

Q2 First, we’re going to summarise the number of likes (favorite_count) CodeClan tweets have. Create a boxplot to check for outliers.
deaths_summarised <- summarise(deaths_grouped, 
                               number_of_deaths = n() )


```{r}
favorite_count_data <- select(twitter_data, favorite_count)
favorite_count_data
```

```{r}
favorite_count_summary <- summarise(twitter_data, favorite_count = n())

favorite_count_summary
```

```{r}
boxplot(favorite_count_data)
```


Count the total number of likes (i.e. total of favorite_count), split by media type, and arrange them from most likes to least. Assume that any tweets without a listed media type are of type “text”.
 select(name, allegiances, gender, nobility, year_of_death) %>%
  mutate(years_survived = year_of_death - 298) %>%
  group_by(allegiances) %>%
  summarise(character_count = n()) %>%
  arrange(desc(character_count))
  
  
```{r}
question_5 <- twitter_data %>%
select(favorite_count,media_type) %>%
         group_by(media_type)  %>%
       summarise(favorite_count = n()) %>%
         arrange(desc(favorite_count))

```

```{r}

grouped_favourite_data <- twitter_data %>%
  select(media_type,favorite_count) %>%
  group_by(media_type, favorite_count)


grouped_favourite_data
```

# to remove the na's we can do another line of code.

```{r}
favorite_count_no_na <- drop_na(grouped_favourite_data)


```

# then resummarise, 
#always need to be careful when removing NA's from data set, i.e are we removing pertinent information. what is the reason this data isnt available...


```{r}
summarise(favorite_count_no_na, character_count =n() = )
```
deaths, years_survived = year_of_death
```{r}
grouped_favourite_data <- twitter_data %>%
  select(media_type,favorite_count) %>%
  summarise(favorite_count_no_na, character_count =n()  ) %>%
  arrange(desc(favorite_count))

grouped_favourite_data
 
```

Questio 6.  Find the mean number of characters that a CodeClan tweet contains.

#would like to look at the twitter data again to understand the variables better 

```{r}
names(twitter_data)
```

```{r}
text_twitter_data <- select(twitter_data, tweet_id, text) 



```
# this doesnt work. 
```{r}
mean_character_tweets <- twitter_data %>%
  select(tweet_id, text) %>%
  group_by(tweet_id, text) %>%
  summarise(tweet_id, character_count =n()  ) %>%
  arrange(desc(character_count))
```

```{r}
mean_character_tweets
```



7. The code_clan_info.csv data file contains status_url along with other info. Load this in, and join it to the code_clan_tweets tibble, so that you have a status_url for each tweet. Decide which variable to join the tibbles on.


```{r}
code_clan_info <- read_csv("data/code_clan_info.csv")
code_clan_info
```


```{r}
left_join(twitter_data, code_clan_info, "tweet_id")
```


8. From your new joined data, create a new tibble codeclan_hashtags containing only the tweet_id and hashtags in lowercase for analysis. Keep only those tweets with hashtags.